High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-01 notebooks/intro.qmd
work on benchmarks

### Benchmark

```{julia}
#| output: false
using CounterfactualExplanations.Evaluation: benchmark
bmks = []
for (dataname, dataset) in datasets
    bmk = benchmark(dataset; models=models, generators=generators, suppress_training=true, dataname=dataname)
    push!(bmks, bmk)
end
bmk = reduce(vcat, bmks)
```

@@

>>>>

@@

## Benchmarks

```{julia}
#| output: false
using CounterfactualExplanations.Evaluation: benchmark
bmks = []
measures = [
    CounterfactualExplanations.distance,
    CCE.distance_from_energy,
    CCE.distance_from_targets
]
for (dataname, dataset) in datasets
    bmk = benchmark(
        dataset; 
        models=models, generators=generators, 
        measure=measures,
        suppress_training=true, dataname=dataname,
        n_individuals=10
    )
    push!(bmks, bmk)
end
bmk = reduce(vcat, bmks)
```

```{julia}
#| output: true
#| echo: false
#| label: fig-benchmark
#| fig-cap: "Benchmark results for the different generators."

df = bmk()
plt = data(df) * visual(BoxPlot) * 
    mapping(:generator, :value, row=:variable, col=:dataname, color=:generator)
draw(plt, axis=(xlabel="", xticksvisible=false, xticklabelsvisible=false, width=200, height=180))
```
